\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2022-02-28 expanded-paper-seb-supplementary-material.tex
All files updated for PLOS Feb 28 2022 submission

\input paper-seb-macros.tex

\makeatletter
      \renewcommand{\thefootnote}{\arabic{footnote}}
      {\let\oldbibcite=\bibcite
      % \bibcite{bad-code}{{31}{2020}{{Richards and Boudnik}}{{Richards and Boudnik}}}
      \newcount\mainNumberOfReferences \mainNumberOfReferences=0
      \def\bibcite#1#2{\global\advance\mainNumberOfReferences by 1\oldbibcite{#1}{#2}}
      \IfFileExists{paper-seb-main.aux}{%
      \input paper-seb-main.aux
      }{\typeout{You will need to run Latex on paper-seb-main.tex because we need its aux file}}
      }
\makeatother

@@

%\newpage

@@

%\renewcommand{\thesubsection}{\alph{subsection}}
\def\sectioncontents#1{\immediate\write\contentsfile{\bslash contents{\arabic{section} #1}{\thepage}}}
\def\subsectioncontents#1{\immediate\write\contentsfile{\bslash subcontents{\alph{subsection}\ #1}{\thepage}}}
\def\starredsubsectioncontents#1{\immediate\write\contentsfile{\bslash subcontents{#1}{\thepage}}}

\noindent\vbox{% The table of contents
\def\contents#1#2{\vskip 0mm \noindent{\bfseries #1} \dotfill\ #2\\}
\def\subcontents#1#2{\hbox to 1em{}{#1} \dotfill\ #2\\}
\noindent
\IfFileExists{generated-supplementary.toc}{%
      \input generated-supplementary.toc
      }{\typeout{You will need to run Latex again on paper-seb-supplementary.tex because we need its .toc file}}
}

@@

\item
Clearly, at least while this paper's concepts are tested and mature, SEBs will need to collaborate closely with research organizations, journals, and funding agencies in order to develop incremental developments to policies and processes that will be most effective, and which can be introduced most productively over time to the scientific community at large. Funding agencies may wish to support such strategic work, as they have previously funded one-off projects such as \cite{cosmos}.
\end{enumerate}
There are other ideas to help make SEBs work, but it is clear they are part of the solution. We must not let perfection be the enemy of the good. SEBs don't need to be perfect on day one, but they do need to get going in some shape or form to start making their vital contribution.

@@

\vbox{\noindent\IfFileExists{generated-minicontents.tex}{%
      \input generated-minicontents.tex
      }{\typeout{You will need to run Latex again on paper-seb-supplementary.tex because we need its generated-minicontents.tex file}}}

@@

\bibliography{paper-seb-supplementary-material.bib}

@@

\input generated-example-data.tex

@@

{\sf
\noindent\textbf{Extract from \emph{Royal Society Open Science\/} author guidelines} \\
--- It is a condition of publication that authors make the primary data, materials (such as statistical tools, protocols, software) and code publicly available. These must be provided at the point of submission for our Editors and reviewers for peer-review, and then made publicly available at acceptance. [\ldots] As a minimum, sufficient information and data are required to allow others to replicate all study findings reported in the article. Data and code should be deposited in a form that will allow maximum reuse. As part of our open data policy, we ask that data and code are hosted in a public, recognized repository, with an open licence (CC0 or CC-BY) clearly visible on the landing page of your dataset.

\vskip 3mm
{\raggedleft\scriptsize
\url{royalsociety.org/journals/authors/author-guidelines/#data} \\
accessed 29 July 2020.\par
}

\noindent\textbf{Extract from \emph{Nature Digital Medicine\/} author guidelines}\\
--- A condition of publication in a Nature Research journal is that authors are required to make materials, data, code, and associated protocols promptly available to readers without undue qualifications. [\ldots] A condition of publication in a Nature Research journal is that authors are required to make unique materials promptly available to others without undue qualifications.

{\vskip 3mm\scriptsize
\raggedleft
\url{www.nature.com/nature-research/editorial-policies/reporting-standards#availability-of-data} \\
accessed 29 July 2020.\par
}

\noindent\textbf{Extract from \emph{Lancet Digital Health\/} author guidelines}\\
--- Has detailed data policies, but no code policy.
{\vskip 3mm
\raggedleft\scriptsize
\url{marlin-prod.literatumonline.com/pb-assets/Lancet/authors/tldh-info-for-authors.pdf}
\\
accessed 29 July 2020.\par
}

\noindent\textbf{Extract from \emph{Journal of Vascular Surgery\/} author guidelines}\\
--- Has detailed data policies, but no code policy. While no \emph{Journal of Vascular Surgery\/} papers were surveyed, the following statement on data policies is relevant for section \ref{jvs-policy} in the main paper:

>>>>

% expand paper-seb-macros.tex
% These macros allow the paper and the supplementary material to share a single sequence of bibliography citations

\DeclareUrlCommand\doi{\def\UrlLeft{{\textrm{DOI}}~}}
\DeclareUrlCommand\url{\def\UrlLeft{{\textrm{URL}}~}}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\def\mytitle{Computational science: \hbox{A (fixable) failure of software~engineering}}
%Achieving professional software engineering \hbox{in scientific research}}

\def \citeeg#1{(e.g., \cite{#1})}

\def\inputifexists#1#2{\IfFileExists{#1}{\input{#1}}{\typeout{No file #1. #2}}}

% calculate percentages
\newcount \t
\newcount \tu
\def\pc#1#2{\t = #1%
\multiply \t by 100000%
\divide \t by #2% ?? 0 times percentage
\tu = \t
\divide \t by 1000% percentage, but no idea of remainder
\multiply \t by 1000% 1000 times percentage, with 00 as bottom digits
\advance \tu by -\t% bottom two digits
\divide \t by 1000\relax%
% round to nearest integer
% if ending in > .5 round up
% if ending in exactly .5 round towards nearest even number
\ifnum \tu > 500 % round up
	\advance \t by 1 
\else
	\ifnum \tu = 500 
		\ifodd \t % it's odd, so round up to even number 
			\advance \t by 1
		\else % leave rounded to even number 	
		\fi
	\fi
\fi
\the\t\%}

% insert commas into large numbers
\def\commarise#1{%[#1]
	\t=#1
    \divide \t by 1000
    \ifnum \t > 0
    	\the\t,%
    	\tu=#1
    	\multiply \t by 1000
    	\advance \tu by -\t
		\ifnum \tu < 100 0\fi
		\ifnum \tu < 10 0\fi
		\the\tu
    \else
    	#1%
    \fi
}

% simple macro to use a number register to pluralise (add an s) to words....
% \plural{\t}{fred} => \the\t\ freds if plural, or => one fred if singular
\def\plural#1#2{\ifnum #1=1 
	one #2%
\else
	\the#1\ #2s%
\fi}

% initialisBibliography <title> <starting number> <introductory text>
\newcount\bibciten \bibciten=0
\def\initialiseBibliography#1#2#3{%
	\global\def\refname{#1}
    \global\bibciten=#2
    \global\def\startBibliography{#3}
}

\def\bibskip{\vskip 1ex} % the gap between bib items generated by data.js

% read in any constants defined from the JSON data
% expand generated-constants.tex
\def\journalBreakdown{\emph{Lancet Digital Health\/} ($N=6$), \emph{Nature Digital Medicine\/} ($N=12$) and \emph{Royal Society Open Science\/} ($N=14$)}
\def\tabularJournalBreakdown{&\hbox to 3em {\hfill 6}\hskip 1em \emph{Lancet Digital Health}\\&\hbox to 3em {\hfill 12}\hskip 1em \emph{Nature Digital Medicine}\\&\hbox to 3em {\hfill 14}\hskip 1em \emph{Royal Society Open Science}\\}
\global\newcount \dataN \global\dataN=32
\global\newcount \countAuthors \global\countAuthors=264
\global\newcount \countHasBreach \global\countHasBreach=11
\global\newcount \countHasPolicy \global\countHasPolicy=26
\global\newcount \countUsesVersionControlRepository \global\countUsesVersionControlRepository=10
\global\newcount \counthasDataRepository \global\counthasDataRepository=9
\global\newcount \countNoCodeInRepo \global\countNoCodeInRepo=1
\global\newcount \numberOfJournals \global\numberOfJournals=3
\global\newcount \countCodetested \global\countCodetested=0
\global\newcount \hasDevelopedRigorously \global\hasDevelopedRigorously=0
% end expanding generated-constants.tex
% expand generated-info-for-main.tex
\newlabel{supplementary-material-makefiles}{{2}{11}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{on-code-data-publication}{{3}{14}{XXX}{YYYY}{ZZZZ}}
\newlabel{supplementary-Speigelhalter-section}{{4}{17}{DUMMYA}{DUMMYB}{DUMMYC}}
\def\MaxMainPaperCitationNumber{64}
\newlabel{supplementary-journal-policies-section}{{5}{25}{DUMMYA}{DUMMYB}{DUMMYC}}
\newlabel{supplementary-summary-table}{{5}{30}{DUMMY1}{DUMMY2}{DUMMY3}}
\expandafter\def \csname cite-MetricSelectionFramework\endcsname{[97]}
\expandafter\def \csname cite-PENet\endcsname{[101]}
\expandafter\def \csname cite-PostoperativeOutcomes.RiskNet\endcsname{[103]}
\expandafter\def \csname cite-philter-ucsf\endcsname{[104]}
\expandafter\def \csname cite-AI-CDSS-Cardiovascular-Silo\endcsname{[105]}
\expandafter\def \csname cite-SiameseChange\endcsname{[107]}
\expandafter\def \csname cite-dryad.1g1jwstrw\endcsname{[108]}
\expandafter\def \csname cite-rsos.192210\endcsname{[109]}
\expandafter\def \csname cite-ichHKrWj7hqlznOaR6NQVzITgp40dlqWvWAgAxyafiQ\endcsname{[110]}
\expandafter\def \csname cite-rsos.200566\endcsname{[111]}
\expandafter\def \csname cite-?view.only=87ae173f775b40d79d6cd0fdcf6d4a9c\endcsname{[112]}
\expandafter\def \csname cite-dryad.vx0k6djnr\endcsname{[115]}
\expandafter\def \csname cite-lactModel\endcsname{[116]}
\expandafter\def \csname cite-LRM\endcsname{[118]}
\expandafter\def \csname cite-1\endcsname{[119]}
\expandafter\def \csname cite-manifold-ga\endcsname{[124]}
\expandafter\def \csname cite-blast-ct\endcsname{[126]}
% end expanding generated-info-for-main.tex

\def\supplement{Supplemental Material}
% end expanding paper-seb-macros.tex

\makeatletter
      \renewcommand{\thefootnote}{\arabic{footnote}}
      {\let\oldbibcite=\bibcite
      % example: \bibcite{bad-code}{{31}{2020}{{Richards and Boudnik}}{{Richards and Boudnik}}}
      \newcount\mainNumberOfReferences \mainNumberOfReferences=0
      \def\bibcite#1#2{\global\advance\mainNumberOfReferences by 1\oldbibcite{#1}{#2}}
      % expand paper-seb-main.aux
\relax 
\providecommand\hyper@newdestlabel[2]{}
\providecommand\HyperFirstAtBeginDocument{\AtBeginDocument}
\HyperFirstAtBeginDocument{\ifx\hyper@anchor\@undefined
\global\let\oldcontentsline\contentsline
\gdef\contentsline#1#2#3#4{\oldcontentsline{#1}{#2}{#3}}
\global\let\oldnewlabel\newlabel
\gdef\newlabel#1#2{\newlabelxx{#1}#2}
\gdef\newlabelxx#1#2#3#4#5#6{\oldnewlabel{#1}{{#2}{#3}}}
\AtEndDocument{\ifx\hyper@anchor\@undefined
\let\contentsline\oldcontentsline
\let\newlabel\oldnewlabel
\fi}
\fi}
\global\let\hyper@last\relax 
\gdef\HyperFirstAtBeginDocument#1{#1}
\providecommand*\HyPL@Entry[1]{}
\bibstyle{plos2015}
\citation{abelson}
\HyPL@Entry{0<</S/D>>}
\citation{fixit}
\citation{example-stats}
\citation{Speigelhalter}
\@writefile{toc}{\contentsline {section}{\numberline {1}Introduction}{2}{section.1}\protected@file@percent }
\newlabel{problems}{{1}{2}{Introduction}{section.1}{}}
\citation{Ben,se-bias}
\citation{whitty}
\citation{assurance-case}
\@writefile{toc}{\contentsline {subsection}{\numberline {(1.a)}The role of code in science and scientific publication}{4}{subsection.1.1}\protected@file@percent }
\citation{assessing-quality}
\citation{critiques,diagnosis-reviews}
\citation{knuth}
\citation{science-review}
\citation{diagnosis-reviews}
\citation{tripod}
\citation{diagnosis-reviews}
\@writefile{toc}{\contentsline {subsection}{\numberline {(1.b)}Bugs, code and programming}{5}{subsection.1.2}\protected@file@percent }
\newlabel{knowledge}{{(1.b)}{5}{Bugs, code and programming}{subsection.1.2}{}}
\@writefile{toc}{\contentsline {section}{\numberline {2}State of the art in pandemic modeling}{5}{section.2}\protected@file@percent }
\citation{nature-summary,ICmodel}
\citation{avianFluModel,originalICmodel}
\citation{ICmodel,avianFluModel,originalICmodel}
\citation{tweet}
\citation{ferguson-interview}
\citation{basic-reproducibilty}
\citation{thumbs-up}
\citation{nature-summary,ICmodel}
\citation{codecheck,thumbs-up}
\citation{NVP}
\citation{nvp-ferguson}
\citation{refactoring}
\citation{bad-code}
\citation{pseudo}
\citation{relit}
\citation{nature-review}
\citation{nature-review}
\citation{psychological-modeling}
\citation{psychological-modeling}
\citation{actr}
\@writefile{toc}{\contentsline {subsection}{\numberline {(2.a)}Science beyond epidemiology}{7}{subsection.2.1}\protected@file@percent }
\citation{psychological-modeling}
\citation{Ben,nature-review,se-bias}
\citation{ourReview}
\citation{hamming}
\citation{NVP}
\citation{unfinished}
\citation{unfinished,lancet-unfinished}
\citation{hoare}
\citation{notebooks,popper}
\citation{machine-learning-reproducibility}
\citation{relit}
\citation{ICmodel}
\citation{ICmodel}
\citation{ICmodel}
\citation{flu-model}
\@writefile{lot}{\contentsline {table}{\numberline {1}{\ignorespaces Overview of peer-reviewed paper sample.\relax }}{9}{table.caption.4}\protected@file@percent }
\providecommand*\caption@xref[2]{\@setref\relax\@undefined{#1}}
\newlabel{table-overview}{{1}{9}{Overview of peer-reviewed paper sample.\relax }{table.caption.4}{}}
\@writefile{toc}{\contentsline {section}{\numberline {3}A pilot survey of peer-reviewed research relying on code}{9}{section.3}\protected@file@percent }
\newlabel{survey-section}{{3}{9}{A pilot survey of peer-reviewed research relying on code}{section.3}{}}
\@writefile{toc}{\contentsline {subsection}{\numberline {(3.a)}Methodology}{9}{subsection.3.1}\protected@file@percent }
\@writefile{lot}{\contentsline {table}{\numberline {2}{\ignorespaces Summary of survey results.\relax }}{10}{table.caption.5}\protected@file@percent }
\newlabel{table-summary}{{2}{10}{Summary of survey results.\relax }{table.caption.5}{}}
\@writefile{lot}{\contentsline {table}{\numberline {3}{\ignorespaces Sizes of repositories, with approximate sizes of code (in kLOC) and data for all available GitHub repositories reviewed in the survey, plus \texttt  {covid-sim} \cite  {ICmodel} for comparison. Sizes are approximate because in all repositories code and data are conceptually interchangeable (an issue explained in the Supplemental Material), so choices were made in the survey to avoid double-counting. Many repositories rely on downloading additional code and data, which is not counted in the table as the additional required material is not in the repository cited in the paper. Paper [103]\ has nothing in its repository except a single file still saying ``Code coming soon...'' despite, at the time of cloning and checking repositories, 21\ months had already elapsed since the paper referring to the code was published.\relax }}{11}{table.caption.6}\protected@file@percent }
\newlabel{table-repo-summary}{{3}{11}{Sizes of repositories, with approximate sizes of code (in kLOC) and data for all available GitHub repositories reviewed in the survey, plus \texttt {covid-sim} \cite {ICmodel} for comparison. Sizes are approximate because in all repositories code and data are conceptually interchangeable (an issue explained in the \supplement ), so choices were made in the survey to avoid double-counting. Many repositories rely on downloading additional code and data, which is not counted in the table as the additional required material is not in the repository cited in the paper. Paper \csname cite-PostoperativeOutcomes.RiskNet\endcsname \ has nothing in its repository except a single file still saying ``Code coming soon...'' despite, at the time of cloning and checking repositories, \the \pubdelayinmonths \ months had already elapsed since the paper referring to the code was published.\relax }{table.caption.6}{}}
\citation{open-source}
\citation{stability}
\@writefile{toc}{\contentsline {subsection}{\numberline {(3.b)}Summary of results}{12}{subsection.3.2}\protected@file@percent }
\citation{notebooks}
\citation{cbc}
\@writefile{toc}{\contentsline {section}{\numberline {4}Discussion}{13}{section.4}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {(4.a)}A call to action}{13}{subsection.4.1}\protected@file@percent }
\newlabel{summary}{{(4.a)}{13}{A call to action}{subsection.4.1}{}}
\citation{ethics-code}
\citation{acm-artifacts}
\citation{redmill,iec61508}
\citation{basic-reproducibilty,open-source}
\citation{ABCs-SE}
\citation{lancet-retracted}
\citation{science-lancet1,science-lancet2}
\citation{lancet-learning}
\@writefile{toc}{\contentsline {subsection}{\numberline {(4.b)}Suggestions for further work}{15}{subsection.4.2}\protected@file@percent }
\newlabel{jvs-policy}{{(4.b)}{15}{Suggestions for further work}{subsection.4.2}{}}
\citation{jvs1}
\citation{jvs2,jvs3}
\citation{jvs1}
\citation{numerals}
\citation{fda}
\citation{tweet,ferguson-interview}
\citation{excel-fiasco}
\citation{science-delays}
\citation{whitty}
\@writefile{toc}{\contentsline {section}{\numberline {5}Conclusions}{16}{section.5}\protected@file@percent }
\citation{fixit}
\citation{reproducibility,relit,popper}
\citation{parliamentary-evidence,my-parliamentary-evidence}
\bibdata{paper-seb-main.bib}
\bibcite{abelson}{1}
\bibcite{fixit}{2}
\bibcite{example-stats}{3}
\bibcite{Speigelhalter}{4}
\bibcite{Ben}{5}
\bibcite{se-bias}{6}
\bibcite{whitty}{7}
\bibcite{assurance-case}{8}
\bibcite{assessing-quality}{9}
\citation{assessing-quality-conference}
\bibcite{critiques}{10}
\bibcite{diagnosis-reviews}{11}
\bibcite{knuth}{12}
\bibcite{science-review}{13}
\bibcite{tripod}{14}
\bibcite{nature-summary}{15}
\bibcite{ICmodel}{16}
\bibcite{avianFluModel}{17}
\bibcite{originalICmodel}{18}
\bibcite{tweet}{19}
\bibcite{ferguson-interview}{20}
\bibcite{basic-reproducibilty}{21}
\bibcite{thumbs-up}{22}
\bibcite{codecheck}{23}
\bibcite{NVP}{24}
\bibcite{nvp-ferguson}{25}
\bibcite{refactoring}{26}
\bibcite{bad-code}{27}
\bibcite{pseudo}{28}
\bibcite{relit}{29}
\bibcite{nature-review}{30}
\bibcite{psychological-modeling}{31}
\bibcite{actr}{32}
\bibcite{ourReview}{33}
\bibcite{hamming}{34}
\bibcite{unfinished}{35}
\bibcite{lancet-unfinished}{36}
\bibcite{hoare}{37}
\bibcite{notebooks}{38}
\bibcite{popper}{39}
\bibcite{machine-learning-reproducibility}{40}
\bibcite{flu-model}{41}
\bibcite{open-source}{42}
\bibcite{stability}{43}
\bibcite{cbc}{44}
\bibcite{ethics-code}{45}
\bibcite{acm-artifacts}{46}
\bibcite{redmill}{47}
\bibcite{iec61508}{48}
\bibcite{ABCs-SE}{49}
\bibcite{lancet-retracted}{50}
\bibcite{science-lancet1}{51}
\bibcite{science-lancet2}{52}
\bibcite{lancet-learning}{53}
\bibcite{jvs1}{54}
\bibcite{jvs2}{55}
\bibcite{jvs3}{56}
\bibcite{numerals}{57}
\bibcite{fda}{58}
\bibcite{excel-fiasco}{59}
\bibcite{science-delays}{60}
\bibcite{reproducibility}{61}
\bibcite{parliamentary-evidence}{62}
\bibcite{my-parliamentary-evidence}{63}
\citation{parliamentary-evidence}
\bibcite{assessing-quality-conference}{64}
\newlabel{LastPage}{{}{22}{}{page.22}{}}
\xdef\lastpage@lastpage{22}
\xdef\lastpage@lastpageHy{22}
\gdef \@abspage@last{22}
% end expanding paper-seb-main.aux
      }
\makeatother

@@

@@

\def\sectioncontents#1{\immediate\write\contentsfile{\bslash contents{\arabic{section} #1}{\thepage}}}
\def\subsectioncontents#1{\immediate\write\contentsfile{\bslash subcontents{\alph{subsection}\ #1}{\thepage}}}
\def\starredsubsectioncontents#1{\immediate\write\contentsfile{\bslash subcontents{#1}{\thepage}}}

\noindent\vbox{% The table of contents
\def\contents#1#2{\vskip 0mm \noindent{\bfseries #1} \dotfill\ #2\\}
\def\subcontents#1#2{\hbox to 1em{}{#1} \dotfill\ #2\\}
\noindent
% expand generated-supplementary.toc
\contents{1 Further issues for Software Engineering Boards (SEBs)}{3}
\subcontents{a\ {Brief definition}}{3}
\subcontents{b\ Relationships of SEBs to Ethics Boards}{4}
\subcontents{c\ {SEBs are necessary but not sufficient}}{5}
\contents{2 Software engineering best practice}{5}
\subcontents{a\ Introduction and standard references}{5}
\subcontents{b\ Essential components of best practice}{6}
\subcontents{\hbox to \howwide {\hfill (0)} Requirements}{6}
\subcontents{\hbox to \howwide {\hfill (1)} {Formal methods}}{6}
\subcontents{\hbox to \howwide {\hfill (2)} Defensive programming}{8}
\subcontents{\hbox to \howwide {\hfill (3)} {Using dependable programming languages}}{8}
\subcontents{\hbox to \howwide {\hfill (4)} Open source and version control}{8}
\subcontents{\hbox to \howwide {\hfill (5)} Rigorous testing}{10}
\subcontents{\hbox to \howwide {\hfill (6)} {Good documentation and record keeping}}{10}
\subcontents{\hbox to \howwide {\hfill (7)} Usability}{11}
\subcontents{\hbox to \howwide {\hfill (8)} Reusing quality solutions}{12}
\subcontents{\hbox to \howwide {\hfill (9)} Simplicity}{12}
\subcontents{\hbox to \howwide {\hfill (10)} {Compliance with standards}}{13}
\subcontents{\hbox to \howwide {\hfill (11)} Effective multidisciplinary teamwork}{13}
\subcontents{\hbox to \howwide {\hfill (12)} {Continuous Professional Development (CPD)}}{13}
\subcontents{\hbox to \howwide {\hfill (13)} {Security and other factors}}{14}
\contents{3 Code, data and publication}{14}
\contents{4 {The Speigelhalter trustworhiness questions}}{17}
\subcontents{a\ {How trustworthy are the numbers?}}{17}
\subcontents{b\ {How trustworthy is the source?}}{18}
\subcontents{c\ {How trustworthy is the interpretation?}}{18}
\contents{5 {Summary of pilot survey}}{21}
\subcontents{a\ {Assessment criteria and methods}}{21}
\subcontents{b\ {Detecting and defending against error}}{24}
\subcontents{c\ {Code policies of sampled journals}}{25}
\subcontents{d\ {Assessments and criteria}}{26}
\subcontents{e\ {Summary of assessments}}{30}
\subcontents{f\ {References for sampled papers}}{31}
% end expanding generated-supplementary.toc
}

@@

\item
Clearly, at least while this paper's concepts are tested and mature, SEBs will need to collaborate closely with research organizations, journals, and funding agencies in order to develop incremental developments to policies and processes that will be most effective, and which can be introduced most productively over time to the scientific community at large. Funding agencies may wish to support such strategic work, as they have previously funded one-off projects such as \cite{cosmos}.
\end{enumerate}

There are other ideas to help make SEBs work, but it is clear they are part of the solution. We must not let perfection be the enemy of the good. SEBs don't need to be perfect on day one, but they do need to get going in some shape or form to start making their vital contribution.

@@

\vbox{\noindent
      % expand generated-minicontents.tex
\nnInContents{0}{Requirements}
\nnInContents{1}{{Formal methods}}
\nnInContents{2}{Defensive programming}
\nnInContents{3}{{Using dependable programming languages}}
\nnInContents{4}{Open source and version control}
\nnInContents{5}{Rigorous testing}
\nnInContents{6}{{Good documentation and record keeping}}
\nnInContents{7}{Usability}
\nnInContents{8}{Reusing quality solutions}
\nnInContents{9}{Simplicity}
\nnInContents{10}{{Compliance with standards}}
\nnInContents{11}{Effective multidisciplinary teamwork}
\nnInContents{12}{{Continuous Professional Development (CPD)}}
\nnInContents{13}{{Security and other factors}}
% end expanding generated-minicontents.tex
      }

@@

% expand bibliography paper-seb-supplementary-material.bbl
\begin{thebibliography}{10}

\bibitem{vancouver}
{Vancouver Group}.
\newblock Uniform requirements for manuscripts submitted to biomedical
  journals.
\newblock JAMA. 1997;277(11):927--934.
\newblock doi:{10.1001/jama.1997.03540350077040}.

\bibitem{cosmos}
Stepney S, Polack FAC, Alden K, Andrews PS, Bown JL, Droop A, et~al.
\newblock Engineering Simulations as Scientific Instruments: A Pattern
  Language.
\newblock Springer; 2018.

\bibitem{ai-ethics}
Misselhorn C.
\newblock Artificial Morality. {Concepts}, Issues and Challenges.
\newblock Social Science and Public Policy. 2018;55:161--169.
\newblock doi:{10.1007/s12115-018-0229-y}.

\bibitem{sommerville}
Sommerville I.
\newblock Software Engineering.
\newblock 10th ed. Pearson; 2015.

\bibitem{knight}
Knight J.
\newblock Fundamentals of Dependable Computing for Software Engineers.
\newblock CRC Press; 2012.

\bibitem{wpf}
Zeller A.
\newblock Why Programs Fail: A Guide to Systematic Debugging.
\newblock Morgan Kaufmann; 2006.

\bibitem{humphrey}
Humphrey WS.
\newblock PSP: A Self-Improvement Process for Software Engineers.
\newblock Addison Wesley; 2005.

\bibitem{managers}
Humphrey WS.
\newblock Winning with Software: An Executive Strategy.
\newblock Addison-Wesley Professional; 2001.

\bibitem{heedless}
Thimbleby H.
\newblock Heedless Programming: Ignoring Detectable Error is a Widespread
  Hazard.
\newblock Software --- Practice {\&} Experience. 2012;42(11):1393--1407.
\newblock doi:{10.1002/spe.1141}.

\bibitem{plos}
Chao DL, Halloran ME, Obenchain VJ, {Longini Jr} IM.
\newblock FluTE, a Publicly Available Stochastic Influenza Epidemic Simulation
  Model.
\newblock PLOS Computational Biology. 2010;6(1):e1000656.
\newblock doi:{10.1371/journal.pcbi.1000656}.

\bibitem{excel1}
Abir M, Nelson C, Chan EW, Al-Ibrahim H, Cutter C, Patel K, et~al.
\newblock RAND Critical Care Surge Response Tool: An Excel-Based Model for
  Helping Hospitals Respond to the COVID-19 Crisis.
\newblock RAND Corporation; 2020.
\newblock Available from: \url{www.rand.org/pubs/tools/TLA164-1.html}.

\bibitem{excel2}
Alvarez NM, Gonzalez-Gonzalez E, Trujillo-de Santiago G.
\newblock Modeling {COVID-19} epidemics in an Excel spreadsheet:
  {Democratizing} the access to first-hand accurate predictions of epidemic
  outbreaks.
\newblock MedRxiv. 2020;doi:{10.1101/2020.03.23.20041590}.

\bibitem{npm}
Schlueter IZ.
\newblock Blog: kik, left-pad, and npm.
\newblock NPM Blog; 23 March 2016.
\newblock Available from:
  \url{blog.npmjs.org/post/141577284765/kik-left-pad-and-npm}.

\bibitem{LP}
Knuth DE.
\newblock Literate programming. vol.~27.
\newblock Center for the Study of Language and Information Publication Lecture
  Notes; 1992.

\bibitem{hci1}
Shneiderman B, Plaisant C, Cohen M, {\emph{et al}}.
\newblock Designing the User Interface: Strategies for Effective Human-Computer
  Interaction.
\newblock 6th ed. Pearson; 2016.
\newblock Available from: \url{www.cs.umd.edu/hcil/DTUI6}.

\bibitem{hci2}
Thimbleby H.
\newblock Press On: Principles of Interaction Programming.
\newblock MIT Press; 2007.

\bibitem{flexibility}
Hanson C, Sussman GJ.
\newblock Software design for flexibility: How to avoid programming yourself
  into a corner.
\newblock MIT Press; 2021.

\bibitem{iso}
{ISO/IEC JTC 1/SC 7 Software and systems engineering Committees}.
\newblock Software engineering --- Guidelines for the application of ISO
  9001:2015 to computer software.
\newblock International Organization for Standardization (ISO); 2015.
\newblock Available from: \url{www.iso.org/standard/74348.html}.

\bibitem{178C}
{RTCA Committee SC-205}.
\newblock DO-178C --- Software Considerations in Airborne Systems and Equipment
  Certification.
\newblock RTCA; 2011.
\newblock Available from: \url{my.rtca.org/NC__Product?id=a1B36000001IcmqEAC}.

\bibitem{peerReview}
Baum T, {Le\ss mann} H, Schneider K.
\newblock The Choice of Code Review Process: A Survey on the State of the
  Practice.
\newblock In: Lecture Notes in Computer Science. vol. 10611 of Product-Focused
  Software Process Improvement: 18th International Conference; 2017. p.
  111--127.

\bibitem{ssi-report}
Brett A, Croucher M, Haines R, Hettrick S, Hetherington J, Stillwell M, et~al.
\newblock State of the Nation Report for Research Software Engineers.
\newblock Research Software Engineer Network; 2017.
\newblock Available from: \url{zenodo.org/record/495360#.Xyfuyi2ZOCM}.

\bibitem{ssi-url}
{Software Sustainability Institute}. Web site; 2020.
\newblock Available from: \url{software.ac.uk}.

\bibitem{security-engineering}
Anderson R.
\newblock Security Engineering.
\newblock 3rd ed. Wiley; 2020.

\bibitem{cyber-cacm}
Shostack A, Zurko ME.
\newblock Secure Development Tools and Techniques Need More Research That Will
  Increase Their Impact and Effectiveness in Practice.
\newblock Communications of the ACM. 2020;63(5):39--41.
\newblock doi:{10.1145/3386908}.

\bibitem{Schneier}
Schneier B.
\newblock Click Here To Kill Everybody --- Security and Survival in a
  Hyper-connected World.
\newblock W. W. Norton {\&} Company, Inc; 2018.

\bibitem{electronic-evidence}
Mason S, Seng D.
\newblock Electronic Evidence.
\newblock 4th ed. Humanities Digital Library; 2017.

\bibitem{viruses}
Thimbleby H, Anderson SO, Cairns P.
\newblock A Framework for Modelling Trojans and Computer Virus Infection.
\newblock Computer Journal. 1999;41(7):444--458.
\newblock doi:{10.1093/comjnl/41.7.444}.

\bibitem{strachey}
Strachey C.
\newblock Fundamental Concepts in Programming Languages.
\newblock Higher-Order and Symbolic Computation. 2000;13:11--49.
\newblock doi:{10.1023/A:1010000313106}.

\bibitem{henderson}
Henderson P.
\newblock Functional Programming: Application and Implementation.
\newblock Computer Science. Prentice-Hall International; 1980.

\bibitem{RMarkdown}
Xie Y, Allaire JJ, Grolemund G.
\newblock R Markdown: The Definitive Guide.
\newblock Chapman {\&} Hall/CRC; 2020.

\bibitem{RS-policy}
Hurst P. The Royal Society -- Data sharing and mining; 2022.

% end expanding bibliography paper-seb-supplementary-material.bbl

@@

% expand generated-example-data.tex
\def\countFields{30}
\noindent\texttt{
\hspace*{2em}\{\hspace*{2em}\newline
\hspace*{4em} accessed: "14 July 2020",\newline
\hspace*{4em} doubleChecked: "17 January 2021",\newline
\hspace*{4em} authors: "Callahan A, Steinberg E, Fries JA, Gomba \ldots,\newline
\hspace*{4em} year: 2020,\newline
\hspace*{4em} title: "Estimating the efficacy of symptom-based \ldots,\newline
\hspace*{4em} volume: 3,\newline
\hspace*{4em} number: 95,\newline
\hspace*{4em} journal: "Nature Digital Medicine",\newline
\hspace*{4em} doi: "10.1038/s41746-020-0300-0",\newline
\hspace*{4em} dataComment: "On request",\newline
\hspace*{4em} hasCodeInPrinciple: 1,\newline
\hspace*{4em} codeComment: "``Code is available upon request from th \ldots,\newline
\hspace*{4em} pages: 3\newline
\hspace*{2em}\}
}
% end expanding generated-example-data.tex

@@

\newdimen\tabwidth
\tabwidth=\textwidth
\advance \tabwidth by -4em
\def\specifyurl{\vskip 3mm
\begingroup\raggedleft\scriptsize
} 
\def\specifyurletc#1{\endgroup\\
\hbox{ }\hfill\begin{tabular}{|p{\tabwidth}@{}}
#1
\end{tabular}\vskip .3cm
}

{\sf
\noindent\textbf{Extract from \emph{Royal Society Open Science\/} author guidelines} \\
--- It is a condition of publication that authors make the primary data, materials (such as statistical tools, protocols, software) and code publicly available. These must be provided at the point of submission for our Editors and reviewers for peer-review, and then made publicly available at acceptance. [\ldots] As a minimum, sufficient information and data are required to allow others to replicate all study findings reported in the article. Data and code should be deposited in a form that will allow maximum reuse. As part of our open data policy, we ask that data and code are hosted in a public, recognized repository, with an open licence (CC0 or CC-BY) clearly visible on the landing page of your dataset.}

\specifyurl
\url{royalsociety.org/journals/authors/author-guidelines/#data}
\specifyurletc{Accessed 29 July 2020; the policy has been revised (undated, but accessed 2 February 2022) but retains the same principles; full policy now available via a DOI \cite{RS-policy}. The policy still retains an emphasis on data accessibility, and continues a lack of awareness that code and data are equivalent and often mixed (see section \ref{on-code-data-publication}).}

\noindent\textbf{Extract from \emph{Nature Digital Medicine\/} author guidelines}\\
{\sf --- A condition of publication in a Nature Research journal is that authors are required to make materials, data, code, and associated protocols promptly available to readers without undue qualifications. [\ldots] A condition of publication in a Nature Research journal is that authors are required to make unique materials promptly available to others without undue qualifications.}

\specifyurl
\url{www.nature.com/nature-research/editorial-policies/reporting-standards#availability-of-data}
\specifyurletc{Accessed 29 July 2020; since updated to require [in part] ``Upon publication, Nature Portfolio journals consider it best practice to release custom computer code in a way that allows readers to repeat the published results. Code should be deposited in a DOI-minting repository such as Zenodo, Gigantum or Code Ocean and cited in the reference list following the guidelines described here.'' (accessed 2 February 2022).
}
